\section{Research Experience}

\outerlist{

\entrybig
	{\textbf{University of New Mexico}}{Albuquerque, New Mexico}
	{Research Assistant; Advisor: Prof. Deepak Kapur}
  {Fall 2020 - }
\innerlist{
	\entry{Research on Verification and Formal methods}
	\entryextra{
          Assisted with research on symbolic computation and its application to
          program analysis. 
        }
      }


      \entrybig
      {\textbf{Microsoft Research}}{Redmond, Washington}
      {Research Intern; Mentor: Principal RSDE Mark Marron}
      {Summer 2019}
      \innerlist{
        \entry{Verification in Bosque}
        \entryextra{Developed a prototype of the verification engine for the Bosque 
          programming language in $F^{*}$. Bosque is a language that does not 
          implement loops but offers to programmers transformers
          and functional programming constructions (limited fold operation) to do 
          their programming tasks.}
      }

      \entrybig
      {\textbf{Universidad de las Americas Puebla}}{Cholula, Puebla}
      {Research Student; Advisor: Prof. Mauricio J. Osorio Galindo}{2015-2017}
      \innerlist{
        \entry{Research on Paraconsistent Logics}
        \entryextra{Collaborated with a group of researchers on Paraconsistent
          Logics. My activities included working on some theorems and generate 
          models using the answer set solver Clasp.}
      }

      \entrybig
      {\textbf{Universidad de las Americas Puebla}}{Cholula, Puebla}
      {Intern; Advisor: Prof. Ofelia Cervantes Gutierrez}{Summer 2015}
      \innerlist{
        \entry{Innova4D}
        \entryextra{Analysed and implemented graph algorithms to
          compute Freeman centralities for the development of a recommendation
          system.}
      }

    }
